---
title: "Lab 1"
---

```{r global_options, include=FALSE}
library(knitr)
library(ggplot2)
opts_chunk$set(fig.align="center", fig.height=4, fig.width=5.5)
```

*Enter your name*

**Submit on Canvas as an HTML**


**Problem 1:** Demonstrate basic command of Markdown by creating a bulleted list with three items, a numbered list with three items, and a sentence that has one word in bold and one word in italics.

*Your text goes here.*

**Problem 2:** The `economics` dataset contains various time series data from the US economy:

```{r}
economics
```

Use ggplot to make a line plot of the number of unemployed (column `unemploy`) versus time (column `date`).

```{r}
# your code goes here
```

**Problem 3:** Again using the `economics` dataset, now make a scatter plot (using `geom_point()`) of the number of unemployed versus the personal savings rate (`psavert`), and color points by date.

```{r}
# your code goes here
# economics %>% ggplot(aes(x=unemploy,y=date))+geom_point()
```

**Open problem** Your turn: Again using the `economics` dataset, now make a scatter plot (using `geom_point()`) of the number of `pop` versus `pce`.


```{r}
## Your R code here
## Hint just change the x and y from my code
```
